Exposing Bugs in JavaScript Engines through Test Transplantation and Differential Testing

### 2020-06-13 paper/paper.tex
section 5.1

We prioritized warnings based on their types, reflecting likelihood of
manifesting a real bug. We defined two types---``\hi{}'' and
``\lo{}''.

Warnings of the kind ``\hi{}'' are associated with the cases where the
test code executes without violating any internal checks, but it
violates an assertion declared in the test itself or its harness. The
rationale is that the test data is more likely to be valid in this
case as execution does not raise exceptions in application
code. Warnings of kind ``lo'' cover the remaining cases. These
warnings are more likely to be associated with invalid inputs. They
reflect the cases where the anomaly is observed during the execution
of application functions as opposed to assertions. We observed that
different engines often check pre-conditions of functions
differently. It can happen, for example, that one engine enforces a
weaker pre-condition, compared to another engine, on the inputs of a
function and that is acceptable.\Comment{ For instance, it is
  acceptable to pass values greater than \Fix{x} to function
  \CodeIn{\Fix{WWW}} in \Fix{y} but not in \Fix{z}.} In those cases,
the infrastructure would report a warning that is more likely to be
associated with an invalid input produced by the fuzzer, \ie{}, it is
likely to be a ``bug'' in the test code as opposed to a bug in the
engine. Recall that, for differential testing, we only use seed tests
that pass in all engines.

Despite the problem mentioned above, ``\lo'' warnings can reveal bugs.
Figure~\ref{fig:lo-truepositive} shows one of these cases. In this
example, the test instantiates an \CodeIn{ArrayBuffer} object and
stores an 8-bit integer at the 0 position. According to the
specification~\cite{ecmas262-getviewvalue}, a \CodeIn{RangeError}
exception should be thrown if a negative value is passed to the
function \CodeIn{ToIndex}, indirectly called by the test case from the
function call \CodeIn{getInt8()}. In this case, however, the \chakra{}
engine did not throw any exception, as can be confirmed from the
report that our infrastructure produces starting with text ``Engine
Messages'' at the bottom of Figure~\ref{fig:lo-truepositive}. This is
a case of undocumented precondition. It was fixed by
\chakra\ developers and is no longer present in the most recent
release of \chakra.

@@

\begin{figure}[t!]
  \centering
  \begin{lstlisting}
var buffer = new ArrayBuffer(64);
var view = new DataView(buffer);
view.setInt8(0,0x80);
assert(view.getInt8(-1770523502845470856) === -0x80);

Engines Messages (1:V8, 2:JavaScriptCore, 3:SpiderMonkey):
1. RangeError: Offset is outside the bounds of the DataView
2. RangeError: byteOffset cannot be negative
3. RangeError: invalid or out-of-range index
  \end{lstlisting}
  \caption{\label{fig:lo-truepositive}Example of a ``\lo'' warning
    that led to a confirmed bug report in \chakra. The bug is caused
    by a required precondition check in the implementation of function
    \CodeIn{ToIndex}~\cite{ecmas262-getviewvalue}, which is indirectly called by the test. }
\end{figure}

>>>>

We prioritized warnings based on their likelihood of manifesting a
real bug. We defined two types of warnings based on empirical evidence
weobtained while analyzing bugs. The types ``\hi{}'' and
``\lo{}''. Warnings of the kind ``\hi{}'' are associated with the
cases where the test code executes without violating any internal
checks, but it violates an assertion declared in the test itself or
its harness. The rationale is that the test data is more likely to be
valid in this case as execution does not raise exceptions in
application code. Warnings of kind ``lo'' cover the remaining
cases. These warnings are more likely to be associated with invalid
inputs. They reflect the cases where the anomaly is observed during
the execution of application functions as opposed to assertions. We
observed that different engines often check pre-conditions of
functions differently. It can happen, for example, that one engine
enforces a weaker pre-condition, compared to another engine, on the
inputs of a function and that is acceptable.\Comment{ For instance, it
  is acceptable to pass values greater than \Fix{x} to function
  \CodeIn{\Fix{WWW}} in \Fix{y} but not in \Fix{z}.} In those cases,
the infrastructure would report a warning that is more likely to be
associated with an invalid input produced by the fuzzer, \ie{}, it is
likely to be a ``bug'' in the test code as opposed to a bug in the
engine. Recall that, for differential testing, we only use seed tests
that pass in all engines.

\begin{figure}[h!]
  \centering
  \begin{lstlisting}
var buffer = new ArrayBuffer(64);
var view = new DataView(buffer);
view.setInt8(0,0x80);
assert(view.getInt8(-1770523502845470856) === -0x80);

Message from Engines (1:V8, 2:JavaScriptCore, 3:SpiderMonkey):
1. RangeError: Offset is outside the bounds of the DataView
2. RangeError: byteOffset cannot be negative
3. RangeError: invalid or out-of-range index
  \end{lstlisting}
  \caption{\label{fig:lo-truepositive}Example of a ``\lo'' warning
    that led to a confirmed bug report in \chakra. The bug is caused
    by a required precondition check in the implementation of function
    \CodeIn{ToIndex}~\cite{ecmas262-getviewvalue}, which is indirectly called by the test. }
\end{figure}

Despite the problem mentioned above, ``\lo'' warnings can reveal bugs.
Figure~\ref{fig:lo-truepositive} shows one of these cases. In this
example, the test instantiates an \CodeIn{ArrayBuffer} object and
stores an 8-bit integer at the 0 position. According to the
specification~\cite{ecmas262-getviewvalue}, a \CodeIn{RangeError}
exception should be thrown if a negative value is passed to the
function \CodeIn{ToIndex}, indirectly called by the test case from the
function call \CodeIn{getInt8()}. In this case, however, the \chakra{}
engine did not throw any exception, as can be confirmed from the
report that our infrastructure produces starting with text ``Engine
Messages'' at the bottom of Figure~\ref{fig:lo-truepositive}. This is
a case of undocumented precondition. It was fixed by developers and is
no longer present in the most recent release of the engine.

@@
